% Inference cost + environmental footprint table for the 7-way baseline
% comparison. Numbers derived from sacct (CSCS Clariden, Alps cluster, NVIDIA
% GH200 nodes, last 14 days as of 2026-06-01, COMPLETED jobs > 1 h) and from
% the production-baseline run accounting (each baseline: 112 inits x 10 members
% = 1120 forecasts at 10-day lead). Rates and infrastructure facts verified
% against official CSCS / AIL Lugano sources - see notes block at top of
% memory/MEMORY.md ("Inference cost and environmental footprint, Verified
% sources").
%
% Required packages (already in main preamble per experiments_tables.tex):
%   amsmath, booktabs, xcolor[table], array
%
% Reference via \ref{tab:inference-cost}.
%
% Per-member wall-clock formula: (mean job time in min) / (14 init_times) /
% (10 members) for week-helper jobs. Trained-prob baselines (aifsens, atlas,
% fcn3) here use fewer sample jobs in the 14-day window because their
% production runs completed earlier; the per-job mean is still representative.
%
% Total NH per production-baseline run = 8 week-helper jobs x ~3-4 h x 1 node.
% CHF rate: Swiss academia tier 3 (> 10000 NH/yr) at CHF 3.84/NH, with the
% ETH 25% discount applied: CHF 2.88 / node-hour.
% kWh per NH at GH200 node: peak ~5.6 kW per node (4x Grace-Hopper at ~1 kW
% each plus interconnect), conservative average ~4.0 kW under steady inference
% load, x PUE 1.2 -> ~4.8 kWh per node-hour delivered.

\begin{sidewaystable}[p]
  \centering
  \small
  \setlength{\tabcolsep}{4pt}
  \renewcommand{\arraystretch}{1.20}
  \caption{Per-baseline inference cost on CSCS Alps (NVIDIA GH200; 1 Alps
           node = 4 Grace-Hopper superchips). Per-baseline workload: 1120
           forecasts (112 inits $\times$ 10 members, 10-day lead). The
           s/mbr column is the median pure-inference time per member; CS\,h
           is the wall-clock for a 50-member case-study on one Alps node.
           Cost and energy are computed at CHF 2.88/NH (Swiss-academia tier
           3 with ETH 25\% discount) and 4.0 kW node power $\times$ PUE 1.2;
           full sourcing of metric definitions and rates is in the
           footnotes. Atlas at 38 min/mbr ($\sim$25-40$\times$ slower than
           the other six) reflects its multi-step stochastic-interpolant
           DiT sampler, while the post-hoc baselines (59-125 s/mbr) match
           the single-forward-pass trained-probabilistic baselines.}
  \label{tab:inference-cost}
  \begin{tabular}{@{}l l r r r r r r r r@{}}
    \toprule
    \textbf{Role}
        & \textbf{Model}
        & \textbf{Params}
        & \textbf{Mem$^{\#}$}
        & \textbf{Train$^{\ast}$}
        & \textbf{s/mbr$^{\dag}$}
        & \textbf{CS h$^{\S}$}
        & \textbf{NH$^{\ddag}$}
        & \textbf{CHF$^{\ddag}$}
        & \textbf{kWh$^{\ddag}$} \\
     &  & & \textbf{(GB)} & \textbf{(K GPU-h)} &  &  &  &  &  \\
    \midrule

    \rowcolor{phaseBg}
    \multicolumn{10}{@{}l}{\textbf{Post-hoc weight perturbation} (this work) - shares the underlying deterministic-checkpoint training cost; \emph{zero marginal training cost} for the perturbation itself} \\
    & \mbadge{sfnoC}{sfno\_modes10}       & 573 M  & 2.3  & 4   & \textbf{59}   & 0.20  & 15.3 & 44.1  & 73.4  \\
    \rowcolor{altRow}
    & \mbadge{auroraC}{aurora\_encoder}   & 1.3 B  & 5.2  & 13  & 90            & 0.31  & 23.0 & 66.2  & 110.4 \\
    & \mbadge{graphcastC}{graphcast\_all}  & 37 M   & 0.15 & 22  & 125           & 0.43  & 28.7 & 82.7  & 137.8 \\
    \rowcolor{altRow}
    & \mbadge{aifsC}{aifs\_perturbed}$^{\star\star}$ & 255 M & 1.0 & 11 & $\sim$75 & $\sim$0.26 & $\sim$18 & $\sim$52 & $\sim$88 \\
    \hline

    \rowcolor{phaseBg}
    \multicolumn{10}{@{}l}{\textbf{Trained probabilistic} - requires a separate stochastic-training run beyond the deterministic baseline} \\
    & \mbadge{aifsensC}{AIFS-CRPS}       & 229 M  & 0.9   & 22  & 75            & 0.26  & 18.3 & 52.7  & 87.8  \\
    \rowcolor{altRow}
    & \mbadge{fcn3C}{fcn3}               & 711 M  & 2.8   & 90  & 114           & 0.40  & 26.6 & 76.6  & 127.7 \\
    & \mbadge{atlasC}{atlas}             & 4.3 B  & 17    & -$^{\bullet}$ & \textbf{2280} & \textbf{7.92}  & 43.5 & 125.3 & 208.8 \\
    \rowcolor{altRow}
    & \mbadge{esfmC}{esfm}$^{\ddag\ddag}$ & 110 M  & 0.44  & [ESFM-TRAIN-KGPUH] & [ESFM-SMBR]   & [ESFM-CSH]   & [ESFM-NH]   & [ESFM-CHF]    & [ESFM-KWH]    \\
    \hline

    \rowcolor{phaseBg}
    \multicolumn{10}{@{}l}{\textbf{Classical reference} (off-site)} \\
    & \mbadge{ifsC}{ifs\_ens}          & n/a    & -   & -  & \multicolumn{5}{l}{ECMWF MARS download only; no CSCS compute} \\

    \bottomrule
  \end{tabular}
  \vspace{2pt}

  \scriptsize
  $^{\dag}$\,Pure inference seconds per ensemble member per 10-day forecast
  (excludes data fetch, model load, container startup, zarr write). Mean
  over the 1120-1192 inference calls per baseline, parsed from per-call
  ``Inference starting!''/``Inference complete'' markers in the earth2studio
  logs (median for SFNO, where the mean is inflated by SIGSEGV-recovery
  retries). Atlas estimated from the tqdm progress-bar total (61 rollout
  steps $\times$ 37.5 s/step).
  $^{\S}$\,\textbf{CS h} = wall-clock hours for a 50-member case-study
  forecast on a single Alps node (4 GH200 in parallel):
  $50 \times \text{s/mbr} / 4 / 3600$. Atlas's $\sim$8\,h budget at one
  case-study init is the natural cap on how many case studies are feasible
  within a typical 12\,h SLURM walltime.
  $^{\ddag\ddag}$\,\textbf{esfm} = \citet{Ozdemir2026esfm}, Earth System
  Foundation Model. Aurora 3D Swin U-Net backbone with axial inter-variable
  attention and AdaLN-Zero per-member conditioning, trained on the joint
  MAE\,+\,almost-fair-CRPS objective. The checkpoint used here is
  ESFM\_s\_nm\_10ens at training step 10\,000, an intermediate ensemble-
  finetune snapshot (not a fully trained production model). Production
  training schedule is reported by the authors as
  92\,k (CMIP6 pretrain) $+$ 40\,k (knowledge distillation) $+$ 100\,k
  (ERA5 finetune) $+$ 10\,k (ensemble finetune) steps. Numbers in the
  table are placeholders pending receipt of the swiss-ai training and
  inference logs.
  $^{\star\star}$\,\textbf{aifs\_perturbed} = post-hoc weight perturbation of
  the AIFS v1 deterministic checkpoint at the per-phase winner identified by
  AIFS Phase 1 + Phase 2 ablations (verified 2026-06-01): Phase 2
  \texttt{mag\_0.0275\_layer\_decoder} chosen as the production baseline. AIFS
  is the most decisive multi-metric winner of the four perturb baselines -
  Phase 2 decoder wins 15 of 20 multi-metric cells (CRPS all 4 leads, SSR
  short-mid lead, SSIM and LSD all 4 leads) vs Phase 1's 5 (FSS 95\% all 4
  leads + SSR@240\,h). Production-baseline run (1120 forecasts) is pending;
  the per-member, CS h, NH, CHF, kWh values here are estimates from the
  AIFS-CRPS architectural twin (same forward graph, parameters perturbed
  but not retrained).

  $^{\#}$\,Loaded model size at fp32 ($\sim$param count $\times$ 4 bytes;
  Aurora ckpt file is 4.68 GB at fp32; AIFS .ckpt is anemoi-packaged so
  raw param-byte estimate undercounts by metadata overhead, $\sim$10\%).

  $^{\ast}$\,Single-pass training cost in thousands of GPU-hours, as
  reported by the source paper / model card. Aurora 13K A100-h
  (pretraining 32 $\times$ A100, $\sim$2.5 weeks; fine-tuning not separately
  documented; arXiv:2405.13063). GraphCast 22K TPU v4-hours (32 TPU
  $\times$ 4 weeks; arXiv:2212.12794). SFNO 4K A100-h for the 73-channel
  production checkpoint (256 A100 $\times$ 16\,h; reported in Mahesh
  \& Pathak arXiv:2408.03100, not in the original ICML Bonev et al.\
  2023 paper which describes the architecture). AIFS v1 11K A100-h
  (64 A100 40 GB $\times$ 1 week; arXiv:2406.01465). AIFS-CRPS 22K H100-h
  (128 H100 64 GB $\times$ 7 days, N320 config; arXiv:2412.15832 Table 3).
  FCN3 90K H100-h (Phase 1 only: 1024 H100 $\times$ 78\,h; the full
  three-stage training is more; arXiv:2507.12144).

  $^{\bullet}$\,Atlas training cost is not documented on the model card
  ([huggingface.co/nvidia/atlas-era5](https://huggingface.co/nvidia/atlas-era5)).
  The benchmark paper arXiv:2601.18111 reports inference timings
  (ATLAS-SI: 94 s per 6\,h step on a single A100, i.e.\ 63 min for a
  10-day forecast) but does not give training cost. Our measured 38
  min/mbr on GH200 vs paper's 63 min/mbr on A100 is consistent with
  GH200 being $\sim$1.5x faster than A100 at this workload, so our setup
  is NOT pathologically slow - the cost is structural to the
  stochastic-interpolant DiT's multi-step sampling. NVIDIA also ships
  a faster ATLAS-CRPS variant (3.3 s per 6\,h step, 28x faster than
  ATLAS-SI) but it is a separately-trained CRPS-loss model rather than
  a hyperparameter switch on the same checkpoint.
  $^{\ddag}$\,Per production-baseline run (1120 forecasts).
\end{sidewaystable}
